---
title: "Codebook.md"
output: md_document
---

```{r text, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Week 4 Assignment

The data was collected from the accelerometer and gyroscope in Samsung smartphones of 30 subjects aged 19-48.  The data consists of statistics of the tri-axial linear acceleration (g) and angular velocity (radians/second).  

From the README.txt included with the original data set:

> "The sensor signals (accelerometer and gyroscope) were pre-processed by applyingnoise filters and then sampled in fixed-width sliding windows of 2.56 sec and 50% overlap (128 readings/window). The sensor acceleration signal, which has gravitational and body motion components, was separated using a Butterworth low-pass filter into body acceleration and gravity. The gravitational force is assumed to have only low frequency components, therefore a filter with 0.3 Hz cutoff frequency was used. From each window, a vector of features was obtained by calculating variables from the time and frequency domain."

The accelerometer and gyroscope data was combined with the activity, subject, and names for each of the measurments and reduced to just the measurements of mean and standard deviation.  Finally, the average of each measurement was calculated for each subject/activity pairing.

The table below gives the name, units, class, range, and description of each variable in the final table.

```{r codebook, echo=FALSE}
library(pander)
source('run_analysis.R')

options(width=200)
# Load the accelerometer data
dictionary <- read.csv("../codebook.csv")
pandoc.table(dictionary, justify='lcccl', 
             split.cells = c(15,7,9,6,29))
```
