---
title: "Readme.md"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Week 4 Assignment

You should create one R script called run_analysis.R that does the following:

1. Merges the training and the test sets to create one data set.
   https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip
2. Extracts only the measurements on the mean and standard deviation for each measurement.
3. Uses descriptive activity names to name the activities in the data set
4. Appropriately labels the data set with descriptive variable names.
5. From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

The following code will load the data and issue a call to merge_data().

```{r data}
library(dplyr)
source('run_analysis.R')

# Load the accelerometer data
features <- tbl_df(read.table("../UCI HAR Dataset/features.txt"))
train_data <- tbl_df(read.table("../UCI HAR Dataset/train/X_train.txt"))
test_data <- tbl_df(read.table("../UCI HAR Dataset/test/X_test.txt"))

# Load the activity data
activity_labels <- tbl_df(read.table("../UCI HAR Dataset/activity_labels.txt"))
train_labels <- tbl_df(read.table("../UCI HAR Dataset/train/y_train.txt"))
test_labels <- tbl_df(read.table("../UCI HAR Dataset/test/y_test.txt"))

# Load the subject data
train_subjects <- tbl_df(read.table("../UCI HAR Dataset/train/subject_train.txt"))
test_subjects <- tbl_df(read.table("../UCI HAR Dataset/test/subject_test.txt"))

# Merge the data
merged <- merge_data(features, train_data, test_data, 
                     activity_labels, train_labels, test_labels,
                     train_subjects, test_subjects)
head(merged)
```
