---
title: "Readme.md"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Week 4 Assignment

You should create one R script called run_analysis.R that does the following:

1. Merges the training and the test sets to create one data set.
   https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip
2. Extracts only the measurements on the mean and standard deviation for each measurement.
3. Uses descriptive activity names to name the activities in the data set
4. Appropriately labels the data set with descriptive variable names.
5. From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

The following code will load the data and issue a call to merge_data().

```{r data}
library(dplyr)
source('run_analysis.R')

# Load the accelerometer data
features <- tbl_df(read.table("../UCI HAR Dataset/features.txt"))
train_data <- tbl_df(read.table("../UCI HAR Dataset/train/X_train.txt"))
test_data <- tbl_df(read.table("../UCI HAR Dataset/test/X_test.txt"))

# Load the activity data
activity_labels <- tbl_df(read.table("../UCI HAR Dataset/activity_labels.txt"))
train_labels <- tbl_df(read.table("../UCI HAR Dataset/train/y_train.txt"))
test_labels <- tbl_df(read.table("../UCI HAR Dataset/test/y_test.txt"))

# Load the subject data
train_subjects <- tbl_df(read.table("../UCI HAR Dataset/train/subject_train.txt"))
test_subjects <- tbl_df(read.table("../UCI HAR Dataset/test/subject_test.txt"))

# Merge the data
merged <- merge_data(features, train_data, test_data, 
                     activity_labels, train_labels, test_labels,
                     train_subjects, test_subjects)
head(merged)
```

The accelerometer and gyroscope data was provided in two text files ("X_train.txt" and "X_test.txt") that consisted of `r nrow(train_data)` and `r nrow(test_data)` records respectively, with `r ncol(train_data)` measurements each.  Similarly, two text files ("y_train.txt" and "y_test.txt") provided an activity code for each record and two text files ("subject_train.txt" and "subject_test.txt") provided the subject for each record.  Additionally, a text file ("features.txt") provided a name for each of the measurments.  The files were combined to create one table of size `r nrow(train_data) + nrow(test_data)` x `r ncol(train_data) + 2`.

This table was reduced to just the `r length(c(1,2,grep("*mean\\(|std\\(*",features$V2)+2))` measurements of mean and standard deviation.  Next, a text file ("activity_labels.txt") providing a description for each of the activities was merged with the reduced table and the names for the measurments from "features.txt" was used to provide descriptive names for each of the columns.  Finally, the average of each measurement was calculated for each subject/activity pairing.
